% !TEX program = pdflatex

% Preamble {{{
\documentclass[9pt]{resumetemplate}
\usepackage{enumitem}
\usepackage{amsmath,amssymb,amsfonts}
%\setitemize{itemsep=0.0pt,itemindent=-4pt}
\renewcommand{\labelenumi}{\tiny$\blacksquare$}
 \setlist[enumerate]{
   %labelsep=4pt,
   itemsep=0.0pt,
   topsep=0.0pt,
   %labelindent=10\parindent,
   %itemindent=5pt,
   leftmargin=10pt,
   %before=10pt%\setlength{\listparindent}{-\leftmargin},
 }
% }}}

\begin{document}

% Title {{{
\begin{minipage}[t]{0.45\textwidth}
	\vspace{-\baselineskip}
	% Required for vertically aligning minipages
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{% first name
	  Marcos%
	}}}}}
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{% last name
	  Romero Lamas%
	}}}}}
	
	\vspace{6pt}
	
	{\huge Physicist} % Career or current job title
\end{minipage}
\vspace{0.5cm}
% }}}

% Introduction {{{
\cvsect{Who Am I?}

\begin{minipage}[t]{0.55\textwidth}
	\vspace{-\baselineskip}
	
	% SOME STUFF
	I am currently working in the analysis of LHC$b$ data to measureme the weak 
	$\phi_s$ phase, testing the Standard Model to its limits. This analysis 
	requires a proper selection of the events (which we do using different ML 
	algorithms) and the estimation of different corrections needed to determine
	the most precise value of $\phi_s$ to date. I use python as an interface to
	cuda-C/openCL kernels thus enabling python to use the HPC capabilities of
	GPUs. This is the core of my PhD thesis, which I expect to finish by the end
	of 2021.

\end{minipage}
% Whitespace between
\hfill
%
\begin{minipage}[t]{0.4\textwidth} % 50% of the page for the skills bar chart
	\vspace{-1cm} % Required for vertically aligning minipages
	\icon{MapMarker}{9}{
	\begin{minipage}{\textwidth}
	\phantom{Torreira de Arriba 19\\
	15701, Santiago de Compostela\\}
	Torreira de Arriba 19\\
	15701, Santiago de Compostela\\
  Spain
	\end{minipage}}\\
	\icon{Phone}{9}{+34 600391520}\\
	\icon{At}{9}{\href{mailto:marromlam@gmail.com}{marromlam@gmail.com}}\\	
	\icon{Github}{9}{\href{https://github.com/marromlam}{github.com/marromlam}}\\
  \icon{Linkedin}{9}{\href{www.linkedin.com/in/marcos-romero-lamas}{marcos-romero-lamas}}\\

	% \icon{Globe}{12}{\href{https://alyx.vance.me}{alyx.vance.me}}\\
	% \icon{Twitter}{12}{\href{https://twitter.com/@alyxvance}{@alyxvance}}\\
	% \begin{barchart}{5.5}
	% 	\baritem{JavaScript}{60}
	% 	\baritem{PHP}{100}
	% 	\baritem{SASS/LESS}{70}
	% 	\baritem{Bootstrap}{70}
	% 	\baritem{Git}{40}
	% 	\baritem{LaTeX}{60}
	% \end{barchart}
\end{minipage}


% \begin{center}
% 	\bubbles{5/Eclipse, 6/git, 4/Office, 3/Inkscape, 3/Blender}
% \end{center}

% }}}

% Experience {{{
\cvsect{Experience}

\begin{entrylist}
  \entry
		{Oct. 18 -- \emph{present}}
		{Research Assistant}
		{\href{https://igfae.usc.es/igfae/}{Instituto Galego de Física de Altas Enerxías (IGFAE)}}
    {%
		\vspace{-3mm}
    \begin{enumerate}
      \item Analysis of $B_s^0 \rightarrow J\!/\psi K^+ K^-$ samples to
			determine the world's best measurement of $\phi_s$ oscillation phase of 
			$B_{s}^0$ neutral meson.
			\item Monte Carlo liaison of Charmonia working group simulations. \hfill
			\emph{May 2019 -- (May 2021)}
    \end{enumerate}
    }
  \entry
    {Jan. 17 -- Jul. 17\\\footnotesize{part time}}
    {Research Assistant}
    {\href{https://igfae.usc.es/igfae/}{Instituto Galego de Física de Altas Enerxías (IGFAE)}}
    {%
		\vspace{-3mm}
    \begin{enumerate}
      \item Study of $\mathcal{T}$--odd asymmetries (time reversal) in the
			$B_s^0 \rightarrow K^+ \pi^- K^- \pi^+$ decay through the spin resonance
			of 1 $K{}^{*0}(892)$.
    \end{enumerate}
    }
\end{entrylist}
% }}}

% Education {{{
\cvsect{Education}

\begin{entrylist}
	\entry
		{Oct. 18 -- \emph{present}}
		{\href{https://igfae.usc.es/igfae/es/doctorado/}{PhD in Nuclear and Particle
		Physics}}
		{Universidade de Santiago de Compostela (USC)}
		{}
	\entry
		{Sep. 17 -- Jul. 19}
		{\href{http://m2i.es/en/}{MSc in Industrial Mathematics}}
		{Universidad Politécnica de Madrid (UPM)}
		{Modelling Specialization: Finite Elements, Stochastic Calculus,
		Finances Modeling, Multidisciplinar Design Optimization, Numerical Methods,
		Modelling in Biomedicine, Perturbation Theory... \\
		Dissertation: \emph{GPU--based time--dependent
		angular analysis of $B_s^0 \rightarrow J/\psi K^+K^-$ decay and systematic
		uncertainty validation.}}
	\entry
		{Sep.13 -- Jul. 17}
		{\href{https://www.usc.es/es/centros/fisica/}{Bachelor of Science in
		Physics}}
		{Universidade de Santiago de Compostela (USC)}
		{High Energy Physics Specialization: QFT, Complex Analysis, Algebra, 
		Differential Geometry, Partial Derivatives Equations, Classical and 
		Continuum mediums Mecanics, Solid State, Electronics...\\
		Dissertation: \emph{Study of $T$--odd observables: $B_s^0$--meson decay in
		two neutral vectorial mesons.}}
\end{entrylist}
% }}}

% Complementary Education {{{
\cvsect{Complementary Education}

\begin{entrylist}
  \entry
	  {October 2020\\\footnotesize{\emph{virtual}}}
		{\href{https://indico.cern.ch/event/865287/}{Programming and environments
		for parallelism}}
		{CERN openlab}
		{}
  \entry
	  {June 2020\\\footnotesize{Santiago de Compostela}}
		{\href{https://indico.cern.ch/event/865287/}{Neural Networks: Applications
		to High Energy Physics and Industry}}
		{USC}
		{}
  \entry
	  {January 2020\\\footnotesize{Santiago de Compostela}}
		{\href{https://indico.cern.ch/event/865287/}{Introduction to Quantum
		Computing}}
		{USC}
		{}
  \entry
	  {October 2019\\\footnotesize{Barcelona}}
		{\href{https://indico.ific.uv.es/event/3825/}{1st COMCHA School}}
		{Universitat Ramon--Llul}
		{%
		\vspace{-3mm}
    \begin{enumerate}
      \item Lectures on Artificial Intelligence and Machine Learning
      \item NVIDIA Deep Learning Institute Certificate: Fundamentals of
			Accelerated Computing with CUDA C/C++
    \end{enumerate}
    }
  \entry
	  {Jul. 18 -- Aug. 18\\\footnotesize{Genève}}
		{\href{https://home.cern/summer-student-programme}{CERN Summer School}}
		{Conseil Européen pour la Recherche Nucléaire}
		{%
		\vspace{-3mm}
    \begin{enumerate}
      \item Analysis of LHC$b$ data to make precision measurements on ${K^+}$
			mass.
    \end{enumerate}
    }
%  \entry
%	  {July 2013\\\footnotesize{Santiago de Compostela}}
%		{First Certificate in English (B2)}
%		{The British Council}
%		{}
\end{entrylist}
% }}}

% Talks at conferences {{{
\cvsect{Talks at conferences}
In addition to many talks given at B2CC and LHCb Simulation working groups
weekly meetings, I gave talks at some national and international
conferences.\\[3mm]

\begin{entrylist}
  \entry
	  {October 2020\\\footnotesize{\emph{virtual}}}
		{\href{https://indico.ific.uv.es/event/3825/}{Acceptances and resolutions in
		$B_s^0 \rightarrow J/\!\psi \phi$}}
		{Analysis and Software week}{}
  \entry
	  {October 2019\\\footnotesize{Oviedo}}
		{\href{https://indico.ific.uv.es/event/3825/}{Latest LHCb results on
		$\phi_s$}}
		{CPAN XI days}{}
  \entry
	  {September 2019\\\footnotesize{Perugia}}
		{\href{https://indico.ific.uv.es/event/3825/}{CP violation in beauty and
		charm at LHCb}}
		{KAON 2019}{}
\end{entrylist}
% }}}

% Outreach {{{
\cvsect{Outreach}

\begin{entrylist}
  \entry{March 2021\\\footnotesize{\emph{virtual}}}
    {CMS Masterclass 2021}
    {USC in collaboration with CERN}
    {% Description
    Speaker and instructor during the laboratory sessions as well as
    organiser of the event.
    }
  \entry{March 2020\\\footnotesize{Santiago de Compostela}}
    {CMS Masterclass 2020}
    {USC in collaboration with CERN}
    {% Description
    Speaker and instructor during the laboratory sessions as well as
    organiser of the event.
    }
  \entry
	  {July 2019\\\footnotesize{Santiago de Compostela}}
		{Summer Scientific Campus}
		{USC in collaboration with the Spanish Government}
		{Speaker and instructor during the laboratory sessions.}
  \entry
	  {April 2019\\\footnotesize{Santiago de Compostela}}
    {CMS Masterclass 2019}
    {USC in collaboration with CERN}
    {% Description
    Speaker and instructor during the laboratory sessions.
    }
\end{entrylist}
% }}}

% Publications {{{
\cvsect{Publications}
%\nocite{*}

\begin{entrylist}
  \entry
	  {May 19 - \emph{present}\\\footnotesize{Genève}}
    {LHC$b$ publications}
		{
		\href{https://labs.inspirehep.net/authors/1755373}{Inspire}  /  
    \href{http://cds.cern.ch/record/2627634/}{CERN Document Server}
		}
    {% Description
    To date, \today, I have participated in 
		% \arabic{no_journals} 
		55 scientific papers, where having a main role in: \footnotesize
    \begin{enumerate}
    %  \item \protect\citetitle{Aaij:2019vot},
		%	      \href{https://arxiv.org/abs/1906.08356}
		%				{arXiv:\citefield{Aaij:2019vot}{eprint}}
    \item \textbf{Updated measurement of time-dependent CP-violating observables
		in $B_s^0 \rightarrow J/\!\phi K^+ K^-$ decays},
		    \href{https://arxiv.org/pdf/1906.08356}
				{arXiv:1906.08356v4}
    \end{enumerate}
    }
  \entry{December 2020\\\footnotesize{Santiago de Compostela}}
    {Fast simulation of a forward detector at 50 and 100 TeV proton-proton
		colliders}
		{}
    {% Description
    \textit{V. Chobanova, D. Martínez Santos, C. Prouve, M. Romero Lamas}\\
    We evaluate the performance of an LHCb-like detector using a fast simulation
		of proton-proton collisions at center-of-mass energies of 50 and 100 TeV.
		(...)
    }
  \entry{April 2020\\\footnotesize{Santiago de Compostela}}
    {CP violation in beauty and charm at LHC$b$}
		{}
    {% Description
    \textit{M. Romero Lamas}\\
    The most recent results on CP violation in the decay, mixing and
		interference of both b and c hadrons obtained by the LHCb Collaboration with
		Run I and years 2015-2016 of Run II are presented. (...)}
\end{entrylist}
% }}}

% Languages and IT {{{
\begin{minipage}[t]{0.45\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

\cvsect{Languages}

\emph{Hereinafter R is understood by reading, W by writing and S by oral
communication.}%\\[-1mm]

\begin{description}
  \item[Spanish]  Native
  \item[English]  R(excellent) · W(excellent) · S(very good)
  \item[Portuguese]  R(good) · W (basic) · S (basic)
  \item[Galician]  Native
\end{description}
%\begin{minipage}[t]{0.45\textwidth}
%	\vspace{-\baselineskip}
%	
%	\begin{tabular}{lll}
%	\textbf{Spanish} & \,\,\,\, & Native\\
%	%\textbf{French} & \,\,\,\, & R(basic) · W(rudimentary) · S(rudimentary)\\
%	\textbf{Galician} & \,\,\,\, & Native
%	\end{tabular}
%\end{minipage}
%\hfill
%\begin{minipage}[t]{0.45\textwidth}
%	\vspace{-\baselineskip}
%	
%	\begin{tabular}{lll}
%	\textbf{English} & \,\,\,\, & R(excellent) · W(excellent) · S(very good)\\
%	\textbf{Portuguese} & \,\,\,\, & R(good) · W (basic) · S (basic)\\
%	\end{tabular}
%\end{minipage}
\end{minipage}
%
\hfill
%
\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

\cvsect{IT skills}

\emph{I am a unix-like systems user, who loves Vim to edit code and avoids using
the mouse}

\begin{description}
  \item%
	  [Programming languages]
	  Python (excellent),
	  CUDA-C (very good), OpenCL (very good), C (good), C++ (good),
	  Fortran 90 (basic)
  \item%
	  [Statistical analysis tools]
		ROOT, RooFit, Hydra
  \item
	  [Subject--Specific]
		Matlab (excellent), Mathematica (excellent),
		Origin, LabView, COMSOL
  \item
	  [Markup languages]
	  \LaTeX\, (excellent)
\end{description}
\end{minipage}

% }}}

% Additional information {{{
% \begin{minipage}[t]{1\textwidth}
% 	\vspace{-\baselineskip} % Required for vertically aligning minipages
% 	
% 	\cvsect{Hobbies}
% 	
% 	I love running, rowing and playing paddles on the beach. I like reading 
% 	Wikipedia articles learning about random stuff. I enjoy going out with friends
% 	and tasting wines from all over the world.
% \end{minipage}
%\hfill
%\begin{minipage}[t]{0.45\textwidth}
%	\vspace{-\baselineskip} % Required for vertically aligning minipages
%	
%	\cvsect{Non profit}
%	
%	I help...
%\end{minipage}
% }}}


\end{document}


% vim: ft=tex fdm=marker ts=2 sw=2 sts=2 sr noet
